Active Learning for SAT Solver Benchmarking

### 2022-10-08 paper/paper.tex
added two sections 3.1 and 3.2

\section{Active Learning for SAT Solver Benchmarking}
\label{sec:main}
Our framework follows a simple three-step schema (Alg.~\ref{algALBenchmark}).
%JB: as the algorithm is rather simple and has different parts to be plugged in, I think we should rebrand it as "framework" rather than algorithm (and change the term consistently in text)
%TF: changed
After initializing the model $\mathcal{M}$, we incrementally \emph{select} a problem instance from the pool of instances, one at a time, evaluate the new solver $\hat{a}$ on it, and \emph{update} the model with the acquired result.
We \emph{stop} when meeting some stopping condition.
Since the potential runtime of experiments is by magnitudes larger than the model's update time, we only consider incrementing our benchmark set by one instance at a time rather than using batches.
% For now, we also restrict ourselves to the aforementioned sequential one-instance-at-a-time process.
At the core of the model $\mathcal{M}$ is a prediction function $f\!: \left(\mathcal{A} \cup \left\lbrace \hat{a} \right\rbrace\right) \times \mathcal{I} \rightarrow \mathbb{R}$ that powers the decisions within the previously mentioned three steps.
%Note that the prediction target values may be also a subset of $\mathbb{R}$.
%Refer to the next sections for more details.

\begin{algorithm}
  \caption{Incremental Benchmarking Framework}
  \label{algALBenchmark}

  \KwIn{Instances $\mathcal{I}$, Solvers $\mathcal{A}$, Runtimes $r\!: \mathcal{A} \times \mathcal{I} \rightarrow \left[0, \tau\right]$}
  \KwIn{New Solver $\hat{a} \notin \mathcal{A}$}

  $\mathcal{M} \leftarrow \textrm{init model with $\mathcal{A}$, $\mathcal{I}$, $r$, and $\hat{a}$}$

  $\tilde{\mathcal{I}} \leftarrow \emptyset$

@@

    $\tilde{\mathcal{I}} \leftarrow \tilde{\mathcal{I}} \cup \left\lbrace s \right\rbrace$

@@

  $\operatorname{score}\!\left(\right) \leftarrow \operatorname{predictScores}\!\left(\mathcal{M}\right)$
  %JB: bit confusing that this is not a numerical score, but a function (see next line); maybe call it "score()"? or return a tuple with all estimated scores (one per solver?); also, one could expect to get a benchmark set as result (see title of algorithm), but since instance selection is solver-specific, this is not case (it's rather a benchmarking schema)
  %TF: renamed it to benchmarking framework and score()

  \KwOut{Return tuple of scoring function $\operatorname{score}\!: \mathcal{A} \cup \left\lbrace \hat{a} \right\rbrace \rightarrow \mathbb{R}$ and the selected instances $\tilde{\mathcal{I}}$.}
  %JB: we should formally specify the tuple rather than only describing it in words
  %TF: made it clearer
\end{algorithm}

The following section (Section~\ref{sec:main1}) discusses how we may derive a solver ranking from our model (line~8).
Thereafter, we look at possible sampling criteria (line~4) in Section~\ref{sec:main2} and, finally, possible stopping conditions (line~3) in Section~\ref{sec:main3}.

>>>>

\section{Active Learning for SAT Solver Benchmarking}
\label{sec:main}

In this section, we present the details of our approach.
Section~\ref{sec:main-framework} describes the general procedure.
Section~\ref{sec:main-model} specifies the details of the underlying prediction model.
Section~\ref{sec:main1} discusses how we may derive a solver ranking from that model.
Possible criteria for sampling instances are discussed in Section~\ref{sec:main2}.
Section~\ref{sec:main3} concludes with possible stopping conditions.

\subsection{Incremental Benchmarking Framework}
\label{sec:main-framework}

Our framework follows a simple three-step schema.
Algorithm~\ref{algALBenchmark} outlines the procedure. 
While the stopping condition is not met (line~1), we select \emph{one} problem instance from the pool of instances (line~2) and evaluate the new solver $\hat{a}$ on it (line~3).
We then use the acquired result to update the model (line~4).
When the stopping criterion is met, we return the predicted score of the given solver $\hat{a}$.

\begin{algorithm}
% MI: comment in to rename to framework and remove numbering:
%\SetAlgorithmName{Framework}{framework}{List of Frameworks}
%\renewcommand{\thealgocf}{}
  \caption{Incremental Benchmarking Framework}
  \label{algALBenchmark}

  %\KwIn{Instances $\mathcal{I}$, Solvers $\mathcal{A}$, Runtimes $r\!: \mathcal{A} \times \mathcal{I} \rightarrow \left[0, \tau\right]$}
  \KwIn{Model $\mathcal{M}$,  Solver $\hat{a}$}
  \KwOut{Score of $\hat{a}$}

  \BlankLine

  %$\mathcal{M} \leftarrow \textrm{init model with $\mathcal{A}$, $\mathcal{I}$, $r$, and $\hat{a}$}$
  %$\tilde{\mathcal{I}} \leftarrow \emptyset$

@@

    %$\tilde{\mathcal{I}} \leftarrow \tilde{\mathcal{I}} \cup \left\lbrace s \right\rbrace$

@@

  \Return $\operatorname{predictScore}\!\left(\mathcal{M}, \hat{a}\right)$

  %$\operatorname{score}\!\left(\right) \leftarrow \operatorname{predictScores}\!\left(\mathcal{M}\right)$
  %\KwOut{Return tuple of scoring function $\operatorname{score}\!: \mathcal{A} \cup \left\lbrace \hat{a} \right\rbrace \rightarrow \mathbb{R}$ and the selected instances $\tilde{\mathcal{I}}$.}
\end{algorithm}

\subsection{Solver Model}
\label{sec:main-model}

% MI: describe initialization and update of model

Since the potential runtime of experiments is by magnitudes larger than the model's update time, we only consider incrementing our benchmark set by one instance at a time rather than using batches.
At the core of the model $\mathcal{M}$ is a prediction function $f\!: \left(\mathcal{A} \cup \left\lbrace \hat{a} \right\rbrace\right) \times \mathcal{I} \rightarrow \mathbb{R}$ that powers the decisions within the previously mentioned three steps.
